---
title: "p8105_hw1_tc3326"
author: "KK Chen"
output: github_document 
date: "2024-09-21"
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

Load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

Write a short description of the penguins dataset
```{r}
summary(penguins)
```

* Important variables in this `penguins` dataset include **species**(Adelie, Chinstrap, and Gentoo), **island** names (Biscoe, Dream, Torgersen), **bill length** (ranging from `r min(penguins$bill_length_mm, na.rm = TRUE)` mm to `r max(penguins$bill_length_mm, na.rm = TRUE)` mm), **bill depth**, **flipper length** (mean: `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm), **body mass**, **sex**, and **year** of observation. These important variables' values can be found on the above table. The dataset includes `r nrow(penguins)` rows and `r ncol(penguins)` columns.

Make a scatterplot of flipper length vs bill length 

```{r}
library(ggplot2)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length", x = "Bill Length (mm)", y = "Flipper Length (mm)")
```

```{r}
ggsave("scatterplot_flipper_vs_bill.jpg", width = 6, height = 4)
```

## Problem 2 

create the data frame
```{r}
problem2_df = tibble(
  random_sample = rnorm(10),                       
  logical_vec = rnorm(10) > 0,                   
  char_vec = sample(letters, 10, replace = TRUE),  
  factor_vec = factor(sample(c("Level1", "Level2", "Level3"), 10, replace = TRUE))
)

problem2_df
```

Take the mean of each variable in the dataframe
```{r}
random_sample = pull (problem2_df, var = random_sample)
mean(random_sample)

logical_vec = pull (problem2_df, var =logical_vec)
mean(logical_vec)

char_vec = pull (problem2_df, var =char_vec)
mean(char_vec)

factor_vec = pull (problem2_df, factor_vec)
mean(factor_vec)
```
* The mean **can** be calculated for **numeric**(random_sample) and **logical**(logical_vec) variables.
* The mean **can not** be calculated for **character**(char_vec) and **factor**(factor_vec) variables. 


















